\bf Title

### 2024-02-01 article/paper_padic_spec.tex
ajout definition semialgebrique

The last proposition allows to only consider the resolution of the \ref{DLP} problem.
\begin{proposition}\label{prop:reduc}

	We have then the following results
	\begin{enumerate}

		\item \ref{DLP} have feasible solutions if and only if the $m-r$ last coefficients of $b'$ have nonegative valuation, with $r$ the rank of $S$.
		\item If at least one of the $n-r$ last coefficients of $c'$ is non-zero, if \ref{DLP} admits feasible solutions it is unbounded and does not have a solution.

@@

  Let $M \in \allmat_{d,d}(K)$ with characteristic polynomial $\chi_M = T^d + \sum_{i=0}^{d-1} a_i T^i$ for $a_0,...,a_{d-1} \in K$.
  Firstly, suppose   $M \not \in \allmat_{d,d}^+(K)$ {\it i.e.} $\chi_M$ have a root $\rho$ of negative valuation.
  It follows that $\val \chi_M (\rho) = \val \left(\rho^d+ \sum_{i=0}^{d-1} a_i \rho^i \right) = + \infty$ and $\val \rho^d = d \val \rho <0$.
  The properties of the non-archimedean inequality followed by $\val $ implie that $\val \left( \sum_{i=0}^{d-1} a_i \rho^i\right) = \val \rho^d$ and $\val \left( \sum_{i=0}^{d-1} a_i \rho^i\right) \ge \min \limits_{i=0,..., d-1} \val \left(a_i \rho^i\right)$. Therefore, there exists $i \in \left\{0,...,d-1\right\}$ such that $\val( a_i \rho^i) \le \val\rho^d$ {\it i.e.} such that $\val (a_i) \le (d-i) \val \rho <0$. That is all the results we need to prove the result.

@@

\simone{que peut-on dire de plus de l'ensemble $\allmat_{d,d}^+(K)$ ? normalement c'est un cône non ? peut être
  à cause de \Cref{caracsdp} c'est un $\OK$-cône mais pas un $K$-cône ? ça serait un peu contre-intuitif, mais
  bon, on est sur un corps abstrait.}

@@

@@

\begin{proof}
Let $A$ be the annuli defined by $a<b \in R^*_+$. We consider for all $x,y \in K $ the spectrahedron $\mathcal{S}= \left\{(x,y) \in K  : M(x,y) := \pi^ax \oplus \pi^{-b}y \oplus \begin{bmatrix} \pi^{-1} & -\pi^{-1}x \\ \pi^{-1}y & - \pi^{-1}  \\ \end{bmatrix} \succeq 0\right\}$.

@@

Therefore, if $(x, y)$ verifies \ref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$. The last inequality implies that $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, so $x \in C$.

Reciprocally if $x \in C$ then $(x,x^{-1}) $ is a solution of \ref{eq:annulussyst} .
\end{proof}

>>>>

The last proposition allows us to consider only the case of the \ref{DLP} problem to solve \ref{LP}.
\begin{proposition}\label{prop:reduc}
		\begin{enumerate}
		\item \ref{DLP} have feasible solutions if and only if the $m-r$ last coefficients of $b'$ have nonegative valuation, for $r$ the rank of $S$.
		\item If at least one of the $n-r$ last coefficients of $c'$ is non-zero, if \ref{DLP} admits feasible solutions it is unbounded and does not have a solution.

@@

  Let $M \in \allmat_{d,d}(K)$ with characteristic polynomial $\chi_M = T^d + \sum_{i=0}^{d-1} a_i T^i$ for $a_0,...,a_{d-1} \in K$.
  Firstly, suppose   $M \not \in \allmat_{d,d}^+(K)$ {\it i.e.} $\chi_M$ have a root $\rho$ of negative valuation.
  It follows that $\val \chi_M (\rho) = \val (\rho^d+ \sum_{i=0}^{d-1} a_i \rho^i ) = + \infty$ and $\val \rho^d = d \val \rho <0$.
  The properties of the non-archimedean inequality followed by $\val $ implie that $\val ( \sum_{i=0}^{d-1} a_i \rho^i) = \val \rho^d$ and $\val ( \sum_{i=0}^{d-1} a_i \rho^i) \ge \min_{i=0,..., d-1} \val \left(a_i \rho^i\right)$. Therefore, there exists $i \in \left\{0,...,d-1\right\}$ such that $\val( a_i \rho^i) \le \val\rho^d$ {\it i.e.} such that $\val (a_i) \le (d-i) \val \rho <0$. That is all the results we need to prove the result.

@@

@@

\begin{definition}
  A subset $S$ of $K^n$ is said \emph{semialgebraic} if it is defined by finite unions and intersections of sets defined by polynomial equalities of the form $\{ x \in K^n  : P( x) = 0 \}$ and of sets defined by polynomial inequalities of the form $\{ x\in K^n : \val P(x) \geq 0 \}$.
\end{definition}

\begin{proposition}
  Spectrahedra are semialgebraic sets. 
\end{proposition}

\begin{proof}
  Let $S$ be spectrahedron and $A$ a linear matrix such that $S={x \in K^n : A(x) \succeq 0}$. 
  We denote as $p_i(x)$ the $i$-th coefficient of $\chi_{M(x)}$. The map $p_i	: x \to p_i(x)$ is polynomial and $x \in S$ if and only if $\val(p_i(x)) \geq 0$ for $i=0,...,d$.

  Finally, by \ref{caracsdp}, $S = \{x \in K^n : \chi_{M(x)} \in \OK(T)\} = \bigcap\limits_{i=0}^d \{x \in K^n : \val(p_i(x)) \geq 0\}$.
\end{proof}

@@

\begin{proof}
Let $A$ be the annulus defined by $a<b \in \R^*_+$. We consider for all $x,y \in K $ the spectrahedron $\mathcal{S}= \left\{(x,y) \in K  : M(x,y) := \pi^ax \oplus \pi^{-b}y \oplus \begin{bmatrix} \pi^{-1} & -\pi^{-1}x \\ \pi^{-1}y & - \pi^{-1}  \\ \end{bmatrix} \succeq 0\right\}$.

@@

Therefore, if $(x, y)$ verifies \ref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$. The last inequality implies that $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, so $x \in C$. 
Reciprocally if $x \in C$ then $(x,x^{-1}) $ is a solution of \ref{eq:annulussyst} .
\end{proof}
